\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-12-02 tex/gitlinks.tex
more text, new fig

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/709731d2744831cbf6cc4e9bf5a8473f0c7d29e3/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/709731d2744831cbf6cc4e9bf5a8473f0c7d29e3/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/709731d2744831cbf6cc4e9bf5a8473f0c7d29e3/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/ae47501186fb2c08dfe0ce5e5d8355fab2d9bfad/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/ae47501186fb2c08dfe0ce5e5d8355fab2d9bfad/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/ae47501186fb2c08dfe0ce5e5d8355fab2d9bfad/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}
